Comparing R packages for calculation of persistent homology

### 2020-03-08 tdabench-paper/tdabench.Rmd
updated table content

\begin{table}
\centering
\small
\begin{tabular}{|c|c|c|c|c|}
\hline
Feature & TDA Stats & Dionysus & Gudhi Rips & Gudhi Alpha \\
Dimension & Point Cloud Limit & Point Cloud Limit & Point Cloud Limit & Point Cloud Limit\\
\hline
1 & Not Reached & Not Reached & Not Reached & Not Reached \\ 
2 & Not Reached & 200 points & 280 points & Not Reached \\ 
3 & 300 points & 100 points & 125 points & Could Not Compute \\
4 & 100 points & 50 points & 75 points & Could Not Compute \\ 
\hline
\end{tabular}
\caption{During the benchmarking, certain libraries were not able to calculate persistent homology for sufficiently complex point clouds. 
Limiting factors were point cloud number and feature dimension calculation. 
For Rips complexes, TDA stats had the highest performing capacity among the three Rips libraries. 
Alpha complexes were not computable for any point cloud greater than 3 dimensions, so dimensional features 3 and higher could not be computed.}
\end{table}

>>>>

\begin{table}
\centering
\small
\begin{tabular}{|c|c|c|c|c|}
\hline
Feature & Ripser & Dionysus & Gudhi Rips & Gudhi Alpha \\
Dimension & Point Cloud Limit & Point Cloud Limit & Point Cloud Limit & Point Cloud Limit\\
\hline
1 & Not Reached & Not Reached & Not Reached & Not Reached \\ 
2 & Not Reached & 200 points & 280 points & Not Reached \\ 
3 & 300 points & 100 points & 125 points & Could Not Compute \\
4 & 100 points & 50 points & 75 points & Could Not Compute \\ 
\hline
\end{tabular}
\caption{During the benchmarking, certain libraries were not able to calculate persistent homology for sufficiently complex point clouds. 
Limiting factors were point cloud number and feature dimension calculation. 
For Vietoris-Rips complices, Ripser had the best performing capacity among the three libraries. 
Alpha complexes were not computable for any point cloud greater than 3 dimensions, so dimensional features 3 and higher could not be computed.}
\end{table}
